### 2018-05-30 latex/sc18/prelims.tex
put changes in red

We use $\circ$ to denote the outer product of two or more vectors.
The Hadamard product is the element-wise matrix product and will be denoted using $\Hada$. 
The Khatri-Rao product, abbreviated KRP, will be denoted with $\Khat$. 
Given matrices $\M{A}$ and $\M{B}$ that are $I_{A} \times R$ and $I_{B} \times R$, the KRP $\M{K} = \M{A} \Khat \M{B}$ is $I_{A}I_{B} \times R$. 
It can be thought of as a row-wise Hadamard product, where $\M{K}(i+I_{A}(j{-}1),:) = \M{A}(i,:) \Hada \M{B}(j,:)$, or a column-wise Kronecker product, where $\M{K}(:,c) =  \M{A}(:,c) \Kron \M{B}(:,c)$.

@@

The $n$th mode matricized tensor denoted by $\M{A}_{(n)}$ is a $I_n\times I/I_n$ matrix formed by organizing the $n$th mode fibers of a tensor $\T{X}$ with dimensions $I_{1} \times ... \times I_{N}$ (and $I=\prod I_n$) into the columns of a matrix. 
The Matricized-Tensor Times Khatri-Rao Product or MTTKRP will be central to this work and takes the form $\Mn{M}{n} = \Mz{A}{n} \Mn{K}{n}$, where $\Mn{K}{n}= \Mn{H}{N} \Khat \cdots \Khat \Mn{H}{n+1} \Khat \Mn{H}{n-1} \Khat  \cdots \Khat \Mn{H}{1}$.

@@

%\SplitN{\label{eqn:bcdnncp}}{
$$\HH^{(n)} \leftarrow \argmin_{\HH \geq 0}  \| \Mn{S}{n} \HH^T - {\Mn{M}{n}}^T \|_F^2.$$
%}
The BCD iteration is guaranteed to converge to a stationary point, but there is no guarantee that it converges to a global minimum.
The number of outer iterations to convergence is problem dependent but typically ranges from the 10s to the 1000s.

>>>>

We use $\circ$ to denote the outer product of two or more vectors.
The Hadamard product is the element-wise matrix product and will be denoted using $\Hada$. 
The Khatri-Rao product, abbreviated KRP, will be denoted with $\Khat$. 
Given matrices $\M{A}$ and $\M{B}$ that are $I_{A} \times R$ and $I_{B} \times R$, the KRP $\M{K} = \M{A} \Khat \M{B}$ is $I_{A}I_{B} \times R$. 
It can be thought of as a row-wise Hadamard product, where $\M{K}(i+I_{A}(j{-}1),:) = \M{A}(i,:) \Hada \M{B}(j,:)$, or a column-wise Kronecker product, where \red{$\M{K}(:,c) =  \M{A}(:,c) \Kron \M{B}(:,c)$}.

@@

The $n$th mode matricized tensor denoted by $\M{A}_{(n)}$ is a $I_n\times I/I_n$ matrix formed by organizing the $n$th mode fibers of a tensor $\T{X}$ with dimensions $I_{1} \times ... \times I_{N}$ (and $I=\prod I_n$) into the columns of a matrix. 
The Matricized-Tensor Times Khatri-Rao Product or MTTKRP will be central to this work and takes the form \red{$\Mn{M}{n} = \Mz{A}{n} \Mn{K}{n}$, where $\Mn{K}{n}= \Mn{H}{N} \Khat \cdots \Khat \Mn{H}{n+1} \Khat \Mn{H}{n-1} \Khat  \cdots \Khat \Mn{H}{1}$}.

@@

%\SplitN{\label{eqn:bcdnncp}}{
$$\HH^{(n)} \leftarrow \argmin_{\HH \geq 0}  \| \Mn{S}{n} \HH^T - {\Mn{M}{n}}^T \|_F^2.$$
%}
\red{The BCD iteration is guaranteed to converge to a stationary point, but there is no guarantee that it converges to a global minimum.
The number of outer iterations to convergence is problem dependent but typically ranges from 10s to 1000s.}
